%-----------EXPERIENCE-----------%
\section{Experience}

\companyEntry{Gainsight}{Hyderabad, India}{August 2022 -- Present}{Promoted twice: Associate Software Engineer $\rightarrow$ Software Engineer $\rightarrow$ Senior Software Engineer.}

\roleLine{Senior Software Engineer}{Aug 2025 -- Present}
\resumeItemListStart
\resumeItem{Shipped 5+ enterprise grade features that landed Fortune 500 accounts including Intuit and Adobe, sustained 99.95\% measured uptime across high stakes deployments.}
\resumeItem{Promoted internal APIs to public facing endpoints under proper authorization, enabling customers to integrate the platform into their own systems.}
\resumeItem{Built admin dashboards over 5M+ data points with multi criteria filtering, writes propagate through an event driven pipeline keeping reads consistent within a fraction of a second.}
\resumeItem{Implemented 3 production agents (Moderation, Search, Translation) with stateful multi-step reasoning, tool use, and conditional graph routing -- 95\% decision accuracy on previously manual workflows; CloudWatch observability sustained 99.9\% uptime.}
\resumeItemListEnd

\roleLine{Software Engineer}{Aug 2023 -- Aug 2025}
\resumeItemListStart
\resumeItem{Designed high-throughput APIs serving 2M+ requests/day at $\sim$500 RPS peak with P99 latency under 200ms; drove cost per request down 30\% via caching, architecture iteration, and query plan tuning.}
\resumeItem{Rolled out SSO across the multi-product platform with 5 identity providers (SAML 2, OAuth2, OIDC, Token, Google); replaced per-product credentials with a unified sign-in surface.}
\resumeItem{Extracted 2 team-owned services from the monolith into independently deployable FastAPI microservices with dedicated scaling and CI; cut deployment time from $\sim$30 min to $\sim$10 min and enabled per-service hotfixes.}
\resumeItem{Built the platform's i18n framework supporting 20+ locales with message catalogs, plural rules, and RTL support; unblocked customer launches across EMEA and APAC.}
\resumeItemListEnd

\roleLine{Associate Software Engineer}{Aug 2022 -- Aug 2023}
\resumeItemListStart
\resumeItem{Built a rule based user segmentation engine with multi attribute predicates (registration recency, role, post counts), powers targeted audiences across the platform.}
\resumeItem{Automated CloudFormation IaC for 2 microservices ($\sim$83 AWS resources spanning Lambda, RDS, IAM) with PR driven deploys.}
\resumeItem{Wrote 200+ unit, integration, and E2E tests for critical services; increased coverage from $\sim$40\% to $\sim$75\%, catching regressions pre-merge.}
\resumeItem{Standardized Python local development with Docker Compose across the team's services and gave the team reproducible dev parity with production.}
\resumeItemListEnd
